Conservation of interaction partners between related plants varies widely across communities and between plant families - Supporting Information

### 2019-02-20 manuscript/supporting_info.tex
need to make this a multi-page figure

Supporting information: 1 file containing 4 sections.

@@

@@

\newpage
\section*{Tables}

  \begin{table}[!h]
  \caption{\small Change in log odds (per million years of phylogenetic distance) of a pair of plants in the same family sharing a herbivore.}
  \label{family_slopes_ph}
  \begin{tabular}{|l  rr|}
  \hline
    Family & Change in log odds & $P$-value \\
    \hline
    \emph{Asteraceae} & -1.73 &  0.550 \\
    \emph{Euphorbiaceae} & -19.2 & \textbf{\textless0.001} \\
    \emph{Fabaceae} & 18.7 &  \textbf{0.046} \\
    \emph{Melastomataceae} & -13.2 & \textbf{0.022} \\
    \emph{Moraceae} & -2.13 & 0.092 \\
    \emph{Nothofagaceae} & -595 & \textgreater{0.999} \\
    \emph{Pinaceae} &  -25.8 & 0.733 \\
    \emph{Poaceae} & -4.50 & \textbf{0.020} \\
    \emph{Rubiaceae} & -8.16 &  \textbf{0.006} \\
  \hline
  \end{tabular}
  \smallskip
  \footnotesize

  Nine plant families were sufficiently diverse in our  dataset to permit this analysis
  (see \emph{Materials \\and Methods} for details). For each pattern of overlap, we show the change
  in log odds per million years \\and the associated $P$-value. Statistically significant values are
  indicated in bold. \\

  \end{table}

  \begin{table}[!h]
  \caption{
  \small Change in log odds (per million years of phylogenetic distance) of a pair of plants in the same family sharing a pollinator.}
  \small
  \label{family_slopes_pp}
  \begin{tabular}{|l  rr|}
    \hline
    Family  & Change in log odds & $P$-value \\
    \hline
    \emph{Adoxaceae} &  -65.8 & 0.163 \\
    \emph{Amaryllidaceae} &  -17.9 & \textbf{0.015} \\
    \emph{Apiaceae} &  10.9  & \textbf{0.006} \\
    \emph{Apocynaceae} &  -6.96  & \textbf{0.037} \\
    \emph{Asparagaceae} &  -6.23  & 0.189 \\
    \emph{Asteraceae}* &  -1.47  & \textbf{\textless0.001} \\
    \emph{Berberidaceae} &  -1.48$\times10^3$ & \textgreater0.999 \\
    \emph{Boraginaceae} &  -5.15  & \textbf{\textless0.001} \\
    \emph{Brassicaceae} &  -11.2 & 0.072 \\
    \emph{Calceolariaceae} &  156 & 0.998 \\
    \emph{Campanulaceae} &  334 & 0.999 \\
    \emph{Caprifoliaceae} &  0.310 & 0.959 \\
    \emph{Caryophyllaceae} &  2.09 & 0.644 \\
    \emph{Cistaceae} &  -11.4 & \textbf{\textless0.001} \\
    \emph{Convolvulaceae} &  -1.84  & 0.837 \\
    \emph{Ericaceae} &  4.61 & 0.116 \\
    \emph{Fabaceae}* &  -12.9 & \textbf{\textless0.001} \\
    \emph{Geraniaceae} &  -3.31  & 0.624 \\
    \emph{Hydrangeaceae} &  0.057 & 0.982 \\
    \emph{Iridaceae} &  -27.9 & 0.078 \\
    \emph{Lamiaceae} &  -5.01  & \textbf{\textless0.001} \\
    \emph{Loasaceae} &  -865  & \textgreater0.999 \\
    \emph{Malpighiaceae} &  2.80 & 0.168 \\
    \emph{Malvaceae} &  -5.56  & 0.363 \\
    \emph{Melastomataceae}* &  5.19 & 0.577 \\
    \emph{Montiaceae} &  -1.12  & 0.870 \\
    \emph{Myrtaceae} &  8.55 & 0.071 \\
    \emph{Oleaceae} &  0.995 & 0.855 \\
    \emph{Onagraceae} &  -556  & \textgreater0.999 \\
    \emph{Orchidaceae} &  -14.5 & 0.145 \\
    \emph{Orobanchaceae} &  24.2  & 0.326 \\
    \emph{Papaveraceae} &  -11.2 & 0.511 \\
    \emph{Phyllanthaceae} &  9.99 & 0.433 \\
    \emph{Plantaginaceae} &  -8.48  & \textbf{0.001} \\
    \emph{Poaceae}* &  69.2  & \textbf{0.003} \\
    \emph{Polygonaceae} &  -14.8 & \textbf{\textless0.001} \\
    \emph{Primulaceae} &  14.9  & 0.343 \\
    \emph{Ranunculaceae} &  -38.0 & \textbf{\textless0.001} \\
    \emph{Rosaceae} &  0.759 & 0.735 \\
    \emph{Rubiaceae}* &  -13.0 & \textbf{0.026} \\
    \emph{Salicaceae} &  -1.90  & 0.545 \\
    \emph{Sapindaceae} &  821 & 0.999 \\
    \emph{Saxifragaceae} &  -0.092  & 0.992 \\
    \emph{Solanaceae} &  -21.9 & 0.189 \\
    \emph{Tropaeolaceae} &  192 & 0.997 \\
    \emph{Verbenaceae} &  -9.03  & 0.627 \\
    \emph{Violaceae} &  -0.487  & 0.974 \\
  \hline
  \end{tabular}
  \smallskip
  \footnotesize

    We were able to fit these models to 47 plant families (see \emph{Materials and Methods} for     details). 
    Families \\ marked with an asterisk were also sufficiently diverse in herbivory networks. 
    Statistically significant values \\ are indicated in bold.

    \end{table}

>>>>

@@

  \begin{table}[!h]
    \caption{Original sources for each network used in our analyses.}
    \label{sources}
    \begin{tabular}{|l l l |}
    \hline
    Network & Network type & Original source \\
    \hline
    M\_PL\_001  & Pollination & \citep{Arroyo1982}  \\
    M\_PL\_002  & Pollination & \citep{Arroyo1982}  \\
    M\_PL\_003  & Pollination & \citep{Arroyo1982}  \\
    M\_PL\_004  & Pollination & \citep{Barrett1987} \\
    M\_PL\_005  & Pollination & \citep{Clements1923}  \\
    M\_PL\_006  & Pollination & \citep{Dicks2002} \\
    M\_PL\_007  & Pollination & \citep{Dicks2002} \\
    M\_PL\_008  & Pollination & \citep{Dupont2003}  \\
    M\_PL\_009  & Pollination & \citep{Elberling1999} \\
    M\_PL\_010  & Pollination & Elberling, H. \& Olesen, J. M. Unpublished. \\
    M\_PL\_011  & Pollination & \citep{Olesen2002a}  \\
    M\_PL\_012  & Pollination & Olesen, J. M. Unpublished.  \\
    M\_PL\_013  & Pollination & \citep{Ollerton2003}  \\
    M\_PL\_014  & Pollination & \citep{Hocking1968} \\
    M\_PL\_015  & Pollination & \citep{Petanidou1991} \\
    M\_PL\_016  & Pollination & \citep{Herrera1988} \\
    M\_PL\_017  & Pollination & \citep{Memmott1999} \\
    M\_PL\_018  & Pollination & Olesen, J. M. Unpublished.  \\
    M\_PL\_019  & Pollination & \citep{Inouye1988}  \\
    M\_PL\_020  & Pollination & \citep{Kevan1970} \\
    M\_PL\_021  & Pollination & \citep{Kato1999}  \\
    M\_PL\_022  & Pollination & \citep{Medan2002} \\
    M\_PL\_023  & Pollination & \citep{Medan2002} \\
    M\_PL\_024  & Pollination & \citep{Mosquin1967} \\
    M\_PL\_025  & Pollination & \citep{Motten1982}  \\
    M\_PL\_026  & Pollination & \citep{McMullen1993}  \\
    M\_PL\_027  & Pollination & \citep{Primack1983} \\
    M\_PL\_028  & Pollination & \citep{Primack1983} \\
    M\_PL\_029  & Pollination & \citep{Primack1983} \\
    M\_PL\_030  & Pollination & \citep{Ramirez1992} \\
    M\_PL\_031  & Pollination & \citep{Ramirez1989} \\
    M\_PL\_032  & Pollination & \citep{Schemske1978}  \\
    M\_PL\_033  & Pollination & \citep{Small1976} \\
    M\_PL\_034  & Pollination & \citep{SmithRamirez2005}  \\
    M\_PL\_035  & Pollination & \citep{Percival1974}  \\
    M\_PL\_036  & Pollination & Olesen, J. M. Unpublished.  \\
    \hline
    \end{tabular}

    \clearpage
    \newpage

    \begin{tabular}{|l l l |}
    \hline
    Network & Network type & Original source \\
    \hline
    M\_PL\_037  & Pollination & \citep{Montero2005} \\
    M\_PL\_038  & Pollination & \citep{Montero2005} \\
    M\_PL\_039  & Pollination & \citep{Stald2003} \\
    M\_PL\_040  & Pollination & \citep{Ingversen2006} \\
    M\_PL\_041  & Pollination & \citep{Ingversen2006} \\
    M\_PL\_042  & Pollination & \citep{Philipp2006} \\
    M\_PL\_043  & Pollination & \citep{Montero2005} \\
    M\_PL\_044  & Pollination & \citep{Kato2000}  \\
    M\_PL\_045  & Pollination & \citep{Lundgren2005}  \\
    M\_PL\_046  & Pollination & \citep{Bundgaard2003} \\
    M\_PL\_047  & Pollination & \citep{Dupont2009a}  \\
    M\_PL\_048  & Pollination & \citep{Dupont2009a}  \\
    M\_PL\_049  & Pollination & \citep{Beks2006}  \\
    M\_PL\_050  & Pollination & \citep{Stald2003} \\
    M\_PL\_051  & Pollination & \citep{Vazquez2002} \\
    M\_PL\_052  & Pollination & \citep{Witt1998}  \\
    M\_PL\_053  & Pollination & \citep{Yamazaki2003}  \\
    M\_PL\_054  & Pollination & \citep{Kakutani1990}  \\
    M\_PL\_055  & Pollination & \citep{Kato1996}  \\
    M\_PL\_056  & Pollination & \citep{Kato1993}  \\
    M\_PL\_057  & Pollination & \citep{Inoue1990} \\
    M\_PL\_058  & Pollination & \citep{Bartomeus2008} \\
    M\_PL\_059  & Pollination & \citep{Bezerra2009} \\
    Basset  & Herbivory & \citep{Basset1999}  \\
    Bluthgen  & Herbivory & \citep{Bluthgen2006}  \\
    Bodner  & Herbivory & \citep{Bodner2010}  \\
    Coley & Herbivory & \citep{Coley2006} \\
    Ibanez  & Herbivory & \citep{Ibanez2013}  \\
    Joern\_altuda  & Herbivory & \citep{Joern1979} \\
    Joern\_marathon  & Herbivory & \citep{Joern1979} \\
    Novotny & Herbivory & \citep{Novotny2012} \\
    Peralta & Herbivory & \citep{Peralta2015} \\
    Sheldon & Herbivory & \citep{Sheldon1978} \\
    Ueckert & Herbivory & \citep{Ueckert1971} \\
    \hline
    \end{tabular}
    \end{table}

\clearpage
\newpage

\section*{Supporting information 2: Distributions of $p$-values for permuted networks}

% \begin{figure}[!h]
%     \begin{center}
%       \centerline{\includegraphics*[height=.62\textheight]{Figures/random_p_distributions.eps}}
%     \end{center}
%      \caption{Distributions of $p$-values obtained when comparing the strength of the relationship between niche overlap and phylogenetic distance in 999 permutations of each network in our dataset with 500 permutations of each permuted network. Each line in each panel represents the histogram of $p$-values for one network. Bins are 0.05 wide. Purple lines in panels A-L represent pollination networks while green lines in panels M-N represent plant-herbivore networks. Networks are as follows (darkest to lightest):
%      \textbf{A)} M_PL_001, M_PL_002, M_PL_003, M_PL_004, M_PL_005;
%      \textbf{B)} M_PL_006, M_PL_007, M_PL_008, M_PL_009, M_PL_010;
%      \textbf{C)} M_PL_011, M_PL_012, M_PL_013, M_PL_014, M_PL_015;
%      \textbf{D)} M_PL_016, M_PL_017, M_PL_018, M_PL_019, M_PL_020;
%      \textbf{E)} M_PL_021, M_PL_022, M_PL_023, M_PL_024, M_PL_025;
%      \textbf{F)} M_PL_026, M_PL_027, M_PL_028, M_PL_029, M_PL_030;
%      \textbf{G)} M_PL_031, M_PL_032, M_PL_033, M_PL_034, M_PL_035;
%      \textbf{H)} M_PL_036, M_PL_037, M_PL_038, M_PL_039, M_PL_040;     
%      \textbf{I)} M_PL_041, M_PL_042, M_PL_043, M_PL_044, M_PL_045;
%      \textbf{J)} M_PL_046, M_PL_047, M_PL_048, M_PL_049, M_PL_050;     
%      \textbf{K)} M_PL_051, M_PL_052, M_PL_053, M_PL_054, M_PL_055;
%      \textbf{L)} M_PL_056, M_PL_057, M_PL_058, M_PL_059;
%      \textbf{M)} Ibanez, Joern_altuda, Joern_marathon, Peralta, Sheldon;
%      \textbf{N)} Ueckert, Basset, Bluthgen, Bodner, Coley, Novotny.
%      For original sources for each network, see Table S1.
%      }
%     \label{within_family_regression}
%   \end{figure}

@@
